The \dealii{} Library, Version 9.2

### 2020-06-01 9.2/paper.tex
Avoid a duplicate bibtex entry.

Support for particles was originally introduced in \dealii{} version 9.0. In \dealii,
particles can be used as passive tracers, or as part of more complex
models such as those based on Particle-In-Cells (PIC) approaches \cite{gassmoller2018flexible}.

>>>>

Support for particles was originally introduced in \dealii{} version 9.0. In \dealii,
particles can be used as passive tracers, or as part of more complex
models such as those based on Particle-In-Cells (PIC) approaches \cite{GLHPB18}.
